---
title: "The Transportation Model"
author: "Shivani Pitla"
date: "2022-10-15"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Formulation of LP problem in "R"**

$$ \text{The objective function is } Min\hspace{.3cm} TC = 622(x_11)+614(x_12)+630(x_13)+641(x_21)+645(x_22)+649(x_23) $$
Subject to
$$\text{supply constraints}\\$$
$$(x_11)+(x_12)+(x_13) \le 100$$
$$(x_12)+(x_22)+(x_23) \le 120$$

$$\text{demand constraints}\\$$
$$(x_11)+(x_21) \ge 80$$
$$(x_12)+(x_22) \ge 60$$
$$(x_13)+(x_23) \ge 70$$
$$(x_14)+(x_24) \ge 10$$
$$\text{Non-Negativity constraint}\\$$
$$x_ij \ge 0$$
where
$$i=1,2$$
$$j=1,2$$
*activating the required package and creating the table*
```{r}
library(lpSolve)
tab <- matrix(c(22,14,30,600,100,
                 16,20,24,625,120,
                 80,60,70,"-","-"), ncol=5,byrow=TRUE)
colnames(tab) <- c("warehouse1", "warehouse2", "warehouse3", "ProductionCost", "ProductionCapacity")
rownames(tab) <- c("PlantA", "PlantB", "Demand")
tab <- as.table(tab)
tab
```


```{r}
#Creating dummy variables when supply and demand are not equal
costs <- matrix(c(622,614,630,0,
                  641,645,649,0), ncol = 4, byrow = TRUE)
colnames(costs)<-c("warehouse1","warehouse2","warehouse3","Dummy")
rownames(costs)<-c("PlantA","PlantB")
costs<-as.table(costs)
costs

#Supply Side
row.signs <- rep("<=",2)
row.rhs<- c(100,120)

#Demand Side
col.signs <- rep(">=",4)
col.rhs <- c(80,60,70,10)

#running the lp.transport function 
lptrans <- lp.transport(costs, "min", row.signs, row.rhs, col.signs, col.rhs)


#Getting the objective value
lptrans$objval


#values of all the variables
lptrans$solution
```

\vspace{2mm}
***80 AEDs*** *in Plant B - Warehouse1*\vspace{1mm}\newline
***60 AEDs*** *in Plant A - Warehouse2*\vspace{1mm}\newline
***40 AEDs*** *in Plant A - Warehouse3*\vspace{1mm}\newline
***30 AEDs*** *in Plant B - Warehouse3*\hspace{1mm}*should be created in each facility, supplied to each of the three warehouses of the wholesalers, and then packaged to reduce the overall cost of manufacturing and shipment.*
\vspace{4mm}\newline

***Formulating the dual of the above transportation problem***
\vspace{1mm}\newline

*Since the primary goal was to reduce transportation costs, the secondary goal would be to increase value added (VA).*

$$ {\text Maximize \hspace{3mm} VA = } \hspace{3mm} 80W_1 + 60W_2 + 70W_3 - 100P_A - 120P_B$$
\vspace{1mm}\newline
***Subject to the following constraints***

$$ {\text Total \hspace{2mm} Payments \hspace{2mm} Constraints} $$
$$ W_1 - P_A >= 622 $$
$$ W_2 - P_A >= 614$$
$$ W_3 - P_A >= 630$$
$$ W_1 - P_B >= 641$$
$$ W_2 - P_B >= 645$$
$$ W_3 - P_B >= 649$$
\newline
$${\text Where \hspace{2mm} W_1 = Warehouse \hspace{2mm} 1}$$
$$\hspace{2mm} W_2 = Warehouse \hspace{2mm} 2$$
$$\hspace{2mm} W_3 = Warehouse \hspace{2mm} 3$$
$$\hspace{2mm} P_1 = Plant \hspace{2mm} 1$$
$$\hspace{2mm} P_2 = Plant \hspace{2mm} 2$$
\newline

***Economic Interpretation of the dual***
$$W_1 <= 622 + P_A $$
$$W_2 <= 614 + P_A $$
$$W_3 <= 630 + P_A $$
$$W_1 <= 641 + P_B$$
$$W_2 <= 645 + P_B$$
$$W_3 <= 649 + P_B$$
\newline
$$ \text From \hspace{3mm} the \hspace{3mm} above \hspace{3mm} we \hspace{3mm} can \hspace{3mm} see \hspace{3mm} that \hspace{3mm} W_1 - P_A >= 622$$
\newline
$$ which \hspace{3mm} can \hspace{3mm} be \hspace{3mm} exponented \hspace{3mm} as \hspace{3mm} W_1 <= 622 + P_A$$
\newline
$$ \text here \hspace{3mm} W_1 \hspace{3mm} is \hspace{3mm} considered \hspace{3mm} as \hspace{3mm} the \hspace{3mm} price \hspace{3mm} payments \hspace{3mm} being \hspace{3mm} obtained \hspace{3mm} at \hspace{3mm} the \hspace{3mm} origin \hspace{3mm} which \hspace{3mm} is \hspace{3mm} nothing \hspace{3mm} else, \hspace{3mm}$$ 
$$\text but, \hspace{3mm} the \hspace{3mm} revenue,\hspace{3mm} meanwhile\hspace{3mm} P_A + 622 \hspace{3mm} is \hspace{3mm} the \hspace{3mm} money \hspace{3mm} paid \hspace{3mm} at \hspace{3mm} the \hspace{3mm} origin \hspace{3mm} at \hspace{3mm} Plant_A \hspace{3mm}$$
\newline
$$\text Therefore \hspace{3mm} the \hspace{3mm} equation \hspace{3mm} will \hspace{3mm} be\hspace{3mm} MR_1 >= MC_1.$$
\newline
$$\text To \hspace{3mm} maximize \hspace{3mm} profit \hspace{3mm} ,The \hspace{3mm} Marginal \hspace{3mm} Revenue (MR)\hspace{3mm} should \hspace{3mm}be \hspace{3mm}equal\hspace{3mm} to\hspace{3mm} Marginal\hspace{3mm} Costs(MC)$$
\newline
$$ \text That\hspace{3mm} is,\hspace{3mm}
MR_1 = MC_1$$
\newline
$$\text From \hspace{3mm} th\hspace{3mm} above\hspace{3mm} interpretation,\hspace{3mm} we\hspace{3mm} can\hspace{3mm} say\hspace{3mm} that,$$
$$\text Profit\hspace{3mm} maximization\hspace{3mm} takes\hspace{3mm} place \hspace{3mm} when\hspace{3mm} MC\hspace{3mm} is\hspace{3mm} equal\hspace{3mm} to\hspace{3mm} the\hspace{3mm}MR.$$
\newline

***If MR > MC, we must lower plant expenses in order to achieve the Marginal Revenue (MR).***

\vspace{2mm}
***If MR > MC, we must increase output supply in order to achieve Marginal Revenue (MR).***









